---
title: "prosper-hello_world"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{prosper-hello_world}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Run sensitivity analysis on Well Length using a Horizontal dP friction IPR model

### Load the OpenServer package

```{r setup}
library(rOpenserver)
```


### Enter the well lengths for iteration

```{r}
text_well_length <- "
well_length
500
1000
1500
2000
2500
3000
3500
4000
4500
5000
5500
6000
6500
7000
7500
8000
8500
"

df_wl <- read.table(text = text_well_length, header = TRUE)
df_wl$liquid_rate <- 0
df_wl
```

The table above is equivalent to this sequence:

```{r}
well_length <- 1000
seq(well_length-well_length*50/100, by = well_length*50/100, length.out = 17)
```

### Function to get the model filename
This function will go grab the horizontal well model for analysis.

```{r}
get_prosper_model <- function(model) {
    # get the well model
    models_dir <- system.file("models", package = "rOpenserver")
    model_file <- file.path(models_dir, model)
    if (!file.exists(model_file)) stop("Model not found ...") else
        return(model_file)

}

get_prosper_model(model = "HORWELLDP.OUT")
```

### Start Prosper
```{r}
# Initialize OpenServer
prosper_server <- .OpenServer$new()

# Start Prosper
cmd = "PROSPER.START"
prosper_server$DoCmd(cmd)
```


### Open the model
```{r}
# open Prosper model
model_file <- get_prosper_model(model = "HORWELLDP.OUT")
open_cmd <- "PROSPER.OPENFILE"
open_cmd <- paste0(open_cmd, "('", model_file, "')")
DoCmd(prosper_server, open_cmd)  # using S3 dispatch of R6 class
```


### Iterate through well lengths

```{r}
# iterate through all well length values of interest
i <-  1
for (wlen in df_wl[["well_length"]]) {
  prosper_server$DoSet("PROSPER.SIN.IPR.Single.WellLen", wlen)           # set well length
  prosper_server$DoSet("PROSPER.SIN.IPR.Single.HorizdP[0].ZONLEN", wlen) # set length in zone 1
  prosper_server$DoCmd("PROSPER.anl.SYS.CALC")    # do calculation
  df_wl[["liquid_rate"]][i] <-                       # store liquid rate result in dataframe
    as.double(prosper_server$DoGet("PROSPER.OUT.SYS.RESULTS[0][0][0].SOL.LIQRATE"))
  cat(wlen, df_wl[["liquid_rate"]][i], "\n")
  i <-  i + 1
}

df_wl
```


### Plot the results
```{r}
library(ggplot2)

ggplot(df_wl, aes(x = well_length, y = liquid_rate)) +
  geom_line() +
  geom_point()
```


### Shutdown Prosper

```{r}
# shutdown Prosper
Sys.sleep(3)
command = "PROSPER.SHUTDOWN"
prosper_server$DoCmd(command)
prosper_server <- NULL
```

